Cell type assignments for SCPCP000015

### 2025-02-05 analyses/cell-type-ewings/exploratory_analysis/08-merged-celltypes.Rmd
make tables prettier

# marker genes to be used for validating assignments 
validation_markers_file <- file.path(module_base, "references", "combined-markers.tsv")
```

@@

table(all_info_df$final_annotation)
```
For plotting purposes, we won't show any of the cell types that only have a handful of cells. 
Let's see what cell types we won't be looking at if we only plot the top 9 cell types.

@@

missing_only <- all_info_df |> 
  dplyr::filter(final_annotation %in% missing_celltypes)
table(missing_only$final_annotation)
```

>>>>

# marker genes to be used for validating assignments 
validation_markers_file <- file.path(module_base, "references", "combined-validation-markers.tsv")
```

@@

all_info_df |> 
  dplyr::count(final_annotation) |> 
  dplyr::arrange(desc(n))
```
For plotting purposes, we won't show any of the cell types that only have a handful of cells. 
Let's see what cell types we won't be looking at if we only plot the top 9 cell types.

@@

missing_only <- all_info_df |> 
  dplyr::filter(final_annotation %in% missing_celltypes)

missing_only |> 
  dplyr::count(final_annotation) |> 
  dplyr::arrange(desc(n))
```
